Profitability Prediction of Consulting Projects in the Construction Industry

### 2016-08-26 finalwriteup/draft.rmd
getting paper going

Only three of the model blending techniques used the 8 variables determined above. These were FWLS, Random Forest, and Boosted Trees. The remaining 3 techniques used only the predictions of the three individual models. All six methods were compared against the original Logistic Regression model. Initially 100 train/test runs were performed for each blending method by running 20 iterations of 5-fold cross validation. Summaries of a single example model from each of the blending methods can be found in the Appendix, section 11.3. The AUC results of these iterations are displayed below:

@@

The tested profit curve models can be divided into three categories: original individual methods, simple blends of the individual methods, and complex blends of the individual methods that employed interactions with original features. All original methods did achieve improvements of profit at their optimal thresholds, but did not necessarily consistently improve profits across all cross-folded models. The shaded grey 95% confidence intervals in the Profit Curve plot shows that with the 100 sample models that were analysed, none of the lower bounds for the original methods' were above 100% on the y-axis. That is, it cannot be said with 95% confidence that the original methods' would produce a mean profit higher than historical profits in the given decision framework. This framework stated that projects higher than the optimal thresholds (jobs that are likely to be loss making) should be rejected. Clearly this level of certainty is not beneficial for the case-study business to adopt.

>>>>

Only three of the model blending techniques used the 6 variables determined above. These were FWLS, Random Forest, and Boosted Trees. The remaining 3 techniques used only the predictions of the three individual models. All six methods were compared against the original Logistic Regression model. Initially 100 train/test runs were performed for each blending method by running 20 iterations of 5-fold cross validation. Summaries of a single example model from each of the blending methods can be found in the Appendix, section 11.3. The AUC results of the 100 iterations are displayed below:

@@

The tested profit curve models can be divided into three categories: original individual methods, simple blends of the individual methods, and complex blends of the individual methods that employed interactions with original features. All original methods did achieve improvements of profit at their optimal thresholds, but did not necessarily consistently improve profits across all cross-folded models. The shaded grey 95% confidence intervals in the Profit Curve plot shows that with the 100 sample models that were analysed, none of the lower bounds for the original methods were above 100% on the y-axis. That is, it cannot be said with 95% confidence that the original methods would produce a mean profit higher than historical profits in the given decision framework. This framework stated that projects higher than the optimal thresholds (jobs that are likely to be loss making) should be rejected. Clearly this level of certainty is not beneficial for the case-study business to adopt.
